---
title: "Final Project"
author: "Leonid Sidorov, Vasiliy Zubarev, Yawar Habib"
output:
  pdf_document:
    latex_engine: pdflatex
    toc: yes
    number_sections: yes
    toc_depth: 3
    fig_width: 5
    fig_height: 4
geometry: margin = 2cm
lof: no
fontsize: 10pt
documentclass: article
classoption: a4paper
---

```{r setup, include=FALSE}
# To erase all graphs
graphics.off()
# To erase objects from the working space - Clean up of the memory
rm(list = ls())
# use of the constraint 'set-to-zero' for ANOVAs
options(contrasts=c('contr.treatment','contr.poly'))

suppressPackageStartupMessages(
  {
    library(qtl)
    library(lattice)
    library(tidyverse)
  })
#can also use 'contr.sum' for a 'sum-to-zero' constraint

# postscript figures with colours
trellis.device(device = postscript,color = T)

knitr::opts_chunk$set(echo = TRUE)
```


# Data

Firstly, we import the data.

```{r data_import, echo=TRUE}
QTL_LR4RalstoDataRaw <- read.cross("csvs", genfile="data/LR4_CGPM_avril 2007_geno.csvs", 
                                     phefile="data/LR4_Ralsto_AllScores.csvs", sep=";", dec=",")

#genfile: file containing genotypes, phefile:file containing phenotypes.

QTL_LR4RalstoDataRaw <- convert2riself(QTL_LR4RalstoDataRaw)

#The function convert2riself converts the type of crossing indicating that the analysis was made on RILs obtained by self-fertilization.
summary(QTL_LR4RalstoDataRaw)
```

# ANALYSIS OF THE QUALITY OF PHENOTYPIC AND GENOTYPIC DATA

<!--I took the text from the script QTL_LR5Ralsto_Complete.R, so we will have to change it-->

Graph 1: Evaluation of the quality of genotypic data: visualization of missing data.
Graph 2: Visualization of the genetic map
Graph 3 to 15 (phe 1 to phe 13): Distribution of phenotypic data for the different traits evaluated within the population of RILs

```{r graphic_visualistion, echo=FALSE, fig.align='center', fig.cap=''}
plot(QTL_LR4RalstoDataRaw)
```

Detail of the genetic map.

```{r detail_gen_map, echo=FALSE}
plot.map(QTL_LR4RalstoDataRaw, show.marker.names=TRUE)
```

Details of missing genotypic data.

```{r missing_genotypic_data, echo=FALSE}
plotMissing(QTL_LR4RalstoDataRaw, reorder=TRUE)
```

## Further analysis of the quality of genotypes

Calculation of recombination fractions

```{r rf, echo=FALSE}
QTL_LR4RalstoDataRaw<-est.rf(QTL_LR4RalstoDataRaw)
plotRF(QTL_LR4RalstoDataRaw)
```

The plot above informs us that there is no problem with positioning markers on chromosomes.
